\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
%% Remove draft for real article, put twocolumn for two columns

\newcommand{\vectorproj}[2][]{\mathrm{proj}_{\vect{#1}}\vect{#2}}
\newcommand{\vectorcomp}[2][]{\mathrm{comp}_{\vect{#1}}\vect{#2}}
\newcommand{\vect}{\mathbf}
\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newcommand{\R}{\mathbb{R}}
%% commentary bubble

%% Title 
\title{Homework 6}
\author{ Multivariable Calculus}
%\author[1]{Co-author}
\date{Due: April 10, 2023, 23:59}

\begin{document}

\maketitle

Computational problems are graded for completion, each problem is worth 1 points.

Conceptual problems are graded for correctness, each problem is worth 5 points.

Show all your work to get full credits for each problem.
\section{Computational}
Do the following problems in Stewart's calculus textbook, 8th edition.


Section 14.7: 16-20, 21, 22, 31-38

Section 14.8: 6-10 




\section{Conceptual}

\begin{problem}
    Do the following:
    \begin{enumerate}
        \item Formulate an optimization problem
    to
    find the shortest distance between a point $P_0(x_0,y_0, z_0)$ and
    a plane $Ax + By + Cz = D$.
        \item Solve the above problem.
    \end{enumerate}
\end{problem}

\begin{problem}
    The plane $x+y+2z=2$ intersects the paraboloid $z = x^2 + y^2$ in an ellipse.
    Find the point on this ellipse tat are nearest and farthest from the origin.
\end{problem}

\begin{problem}
    Consider the problem of minimizing the function 
    $f(x,y) = x$ on the curve $y^2 + x^4-x^3 = 0$.
    \begin{enumerate}
        \item Try using the Lagrange multipliers to solve the problem.
        \item Show that the minimum value is $f(0,0) = 0$
            but the Lagrange condition $\nabla f(0,0) = \lambda \nabla g(0,0)$
            is not satisfied for any $\lambda$.
        \item Explain why the Lagrange multipliers fail to find the minimum value in this case.
    \end{enumerate}
\end{problem}

%\bibliography{refs}


\end{document}
